Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
let Emacs's hilighting work.

\begin{quote}\small\begin{verbatim}
[1, 2, 3].reverse.should eq([3, 2, 1])
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
expect {launch_missiles}.to raise_error
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
type Expectation = Assertion
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
x `shouldBe` 23
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
shouldBe :: (Show a, Eq a) => a -> a -> Expectation
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
x `shouldSatisfy` (< 23)
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
shouldSatisfy :: Show a => a -> (a -> Bool)
  -> Expectation
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
launchMissiles >>=
  (`shouldBe` Left "not implemented")
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
launchMissiles `shouldReturn` Left "not implemented"
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
shouldReturn :: (Show a, Eq a) => IO a -> a
  -> Expectation
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
shouldThrow :: Exception e => IO a -> (e -> Bool)
  -> Expectation
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
launchMissiles `shouldThrow` (== ExitFailure 1)
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
launchMissiles `shouldThrow` isPermissionError
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
anyArithException :: ArithException -> Bool
anyArithException = const True
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
evaluate (1 `div` 0) `shouldThrow` anyArithException
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
sort xs == (sort . sort) (xs :: [Int]))
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
\xs -> sort xs == (sort . sort) (xs :: [Int])
\end{verbatim}\end{quote}

>>>>

\begin{quote}
\small
\begin{verbatim}
[1, 2, 3].reverse.should eq([3, 2, 1])
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
expect {launch_missiles}.to raise_error
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
type Expectation = Assertion
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
x `shouldBe` 23
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
shouldBe :: (Show a, Eq a) => a -> a -> Expectation
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
x `shouldSatisfy` (< 23)
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
shouldSatisfy :: Show a => a -> (a -> Bool)
  -> Expectation
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
launchMissiles >>=
  (`shouldBe` Left "not implemented")
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
launchMissiles `shouldReturn` Left "not implemented"
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
shouldReturn :: (Show a, Eq a) => IO a -> a
  -> Expectation
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
shouldThrow :: Exception e => IO a -> (e -> Bool)
  -> Expectation
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
launchMissiles `shouldThrow` (== ExitFailure 1)
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
launchMissiles `shouldThrow` isPermissionError
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
anyArithException :: ArithException -> Bool
anyArithException = const True
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
evaluate (1 `div` 0) `shouldThrow` anyArithException
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
sort xs == (sort . sort) (xs :: [Int]))
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
\xs -> sort xs == (sort . sort) (xs :: [Int])
\end{verbatim}
\end{quote}
